---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<h1 align="center"><code>poorman</code></h1>

<blockquote align="center">
  I'd seen my father. He was a poor man, and I watched him do astonishing things.
    - Sidney Poitier
</blockquote>

## Goal

The goal of `poorman` is to provide base R versions of `dplyr` functions. Check out the blog posts [here](https://nathaneastwood.github.io/tags/poorman/) for more details.

## Installation

`poorman` is still in development and hasn't been published to CRAN yet. You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nathaneastwood/poorman")
```

## Features

`poorman` attempts to replicate the `dplyr` API exactly such that your dplyr code will still run even if you use `poorman` in its place, it even comes with its own `magrittr` pipe (`%>%`) replica. Below are some of the operations that are currently available.

```{r libraries}
library(poorman)
```

### `select()`

```{r select}
mtcars %>% select(mpg, gear, disp)
```

### `filter()`

```{r filter}
mtcars %>% filter(mpg > 28)
```

### `mutate()`

```{r mutate}
mtcars %>% mutate(mpg2 = mpg ^ 2)
```

### `arrange()`

```{r arrange}
mtcars %>% arrange(mpg)
```

### `group_by()`

```{r group_by}
mtcars %>%
  group_by(am, cyl) %>%
  summarise(meanMpg = mean(mpg), sumMpg = sum(mpg))
```

## Related Work

[`bplyr`](https://github.com/yonicd/bplyr) and [`tbltools`](https://github.com/mkearney/tbltools) both attempt to offer similar functionality to this package. Note however that `bplyr` imports `magrittr` and uses `rlang` under the hood and `tbltools` imports `magrittr` and appends `_data` to each of its functions, e.g. `select_data()`. `poorman` attempts to replicate the `dplyr` API exactly without additional packages.
