---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `poorman`

<!-- badges: start -->
<!-- badges: end -->

The goal of poorman is to provide base R versions of `dplyr` functions. Check out the blog post [here](https://nathaneastwood.github.io/2020/02/15/building-a-base-dplyr-with-primitives/) for more details.

## Installation

You can install the released version of poorman from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("poorman")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nathaneastwood/poorman")
```

## Features

`poorman` attempts to replicate the `dplyr` API exactly such that your dplyr code will still run even if you use `poorman` in its place. Below are some of the operations that are currently available.

```{r libraries}
library(poorman)
library(magrittr)
```

### `select()`

```{r select}
mtcars %>% select(mpg, gear, disp)
```

### `filter()`

```{r filter}
mtcars %>% filter(mpg > 28)
```

### `mutate()`

```{r mutate}
mtcars %>% mutate(mpg2 = mpg ^ 2)
```

### `arrange()`

```{r arrange}
mtcars %>% arrange(mpg)
```

### `group_by()`

```{r group_by}
mtcars %>%
  group_by(am, cyl) %>%
  summarise(meanMpg = mean(mpg), sumMpg = sum(mpg))
```
